Dewlap color variation in \textit{Anolis sagrei} is maintained among habitats within islands of the West Indies

### 2021-12-19 ms/sections/discussion.tex
added bit about how different the habitats really are

In this study, we found larger differences among than within islands, a pattern already reported and linked to climatic conditions \citep{Driessens2017} and to densities of predators and of anole congeners \citep{Vanhooydonck2009, Baeckens2018}. Differences among habitats within islands, however, are still difficult to account for. Remaining hypotheses may include, for example, runaway sexual selection \textcolor{olive}{(i.e. arbitrary preferences of females for some colors over others, \citealt{Andersson1994})} \sout{arbitrarily} operating in different directions across islands, but no evidence so far suggests that dewlap is a target of mate choice in anoles \citep{Tokarz2002, Tokarz2005, Lailvaux2006, Nicholson2007}. Another hypothesis is that the different genetic constitutions of different islands, perhaps resulting from founder effects (the islands have been colonized independently, \citealt{vandeSchoot2016} unpubl.; \citealt{Driessens2017, Reynolds2020}), may have predisposed populations to adapt differently to similarly selective circumstances. \textcolor{olive}{That said, signalling can be a multifacetted behavior, and while we focused on dewlap color here, other potentially important elements of behavioral interactions include dewlap size, dewlap patterning, display activity as well as behaviors associated with dewlap extensions such as headbobs and pushups \citep{Vanhooydonck2005, Driessens2014, Driessens2015, Lailvaux2015}. These have been linked in various ways (and not always consistently across studies) not only with environmental variables but also with proxies for sexual selection, predation and species recognition \citep{Vanhooydonck2005, Lailvaux2007, Vanhooydonck2009, Driessens2017, Baeckens2018}, which do vary among islands but may also vary within islands, possibly in interaction with dewlap color.} Either way, new data would be needed to test these hypotheses. \textcolor{olive}{Visual modeling, for instance, would be a valuable follow-up analysis as it would indicate whether the differences we detected may be detectable by the organisms themselves (as has been done in \textit{Anolis} in \citealt{Leal2004, Fleishman2020}), but such approach requires irradiance profiles from the habitats in the field, which we presently do not have.}\\

>>>>

In this study, we found larger differences among than within islands, a pattern already reported and linked to climatic conditions \citep{Driessens2017} and to densities of predators and of anole congeners \citep{Vanhooydonck2009, Baeckens2018}. Differences among habitats within islands, however, are still difficult to account for. Remaining hypotheses may include, for example, runaway sexual selection \textcolor{olive}{(i.e. arbitrary preferences of females for some colors over others, \citealt{Andersson1994})} \sout{arbitrarily} operating in different directions across islands, but no evidence so far suggests that dewlap is a target of mate choice in anoles \citep{Tokarz2002, Tokarz2005, Lailvaux2006, Nicholson2007}. Another hypothesis is that the different genetic constitutions of different islands, perhaps resulting from founder effects (the islands have been colonized independently, \citealt{vandeSchoot2016} unpubl.; \citealt{Driessens2017, Reynolds2020}), may have predisposed populations to adapt differently to similarly selective circumstances. \textcolor{olive}{That said, signalling can be a multifacetted behavior, and while we focused on dewlap color here, other potentially important elements of behavioral interactions include dewlap size, dewlap patterning, display activity as well as behaviors associated with dewlap extensions such as headbobs and pushups \citep{Vanhooydonck2005, Driessens2014, Driessens2015, Lailvaux2015}. These have been linked in various ways (and not always consistently across studies) not only with environmental variables but also with proxies for sexual selection, predation and species recognition \citep{Vanhooydonck2005, Lailvaux2007, Vanhooydonck2009, Driessens2017, Baeckens2018}, which do vary among islands but may also vary within islands, possibly in interaction with dewlap color. Moreover, while the three habitats were clearly recognizable and consistent across islands to the human eye (Fig. \ref{fig:overview}), we did not precisely quantify irradiance within each habitat, and so we may have missed differences between islands.} Either way, new data would be needed to test these hypotheses. \textcolor{olive}{Visual modeling, for instance, would be a valuable follow-up analysis as it would indicate whether the differences we detected may be detectable by the organisms themselves (as has been done in \textit{Anolis} in \citealt{Leal2004, Fleishman2020}), but such approach requires irradiance profiles from the habitats in the field, which we presently do not have.}\\
